Stochastic Variance-Reduced Policy Gradient

### 2018-02-07 svrpg.tex

\subsection{Normalized Importance Sampling}\label{sec:prac}
As we already mentioned in section \ref{sec:stopping} importance weights means a lot of variance to deal with. Therefore, in oreder to cope with this issue the literature propose the Self-normalization techniques \cite{precup2000eligibility}.
This technique offers a variance reduction over the importance weights in exchange of a bias introduction. Hence, if the bias introduced by this is smaller than the variance reduction it causes, it is convenient to use it in practice.  We expirienced some improvements using it (see section \ref{sec:exp} for the sperimental point of view).
Self-normalization is easy to use, but depends on the chosen reinforcement learning algorithm. Therefore, here we give the definition of this technique in the context of G(PO)MDP where we have used the weighted per-decision importance sampling estimator \cite{precup2000eligibility}:
\begin{align*}
\gradApp{\vtheta}{N} = \frac{1}{\Omega}\sum_{n=1}^{N}\sum_{h=0}^{H-1}\left(\sum_{k=0}^{h}\score{\vtheta}{a_k^n\vert s_k^n}\right)\left(\gamma^h r_h^n \omega(z_{0:h})\right).
\end{align*} 
where:
\begin{align*}
\omega(z_{0:h}) = \prod_{k=0}^{h} \frac{\pi_{\vtheta}({a_k^n\vert s_k^n})
 }{\pi_{\vtheta^{'}}({a_k^n\vert s_k^n})}
\end{align*}
\begin{align*}
\Omega = \sum_{n=1}^{N}\sum_{h=0}^{H-1}\gamma^h\prod_{k=0}^{h} \frac{\pi_{\vtheta}({a_k^n\vert s_k^n})
}{\pi_{\vtheta^{'}}({a_k^n\vert s_k^n})}
\end{align*}
\todomat{why should we use it? What advantages do we expect? At what cost? Pointer to experiments}

>>>>

\subsection{Normalized Importance Sampling}\label{sec:prac}
As we already mentioned in section \ref{sec:stopping} importance weights means a lot of variance to deal with. Therefore, in order to cope with this issue the literature propose the Self-normalization technique.
This technique offers a variance reduction over the importance weights in exchange of a bias introduction. Hence, if the bias introduced by this is smaller than the variance reduction it causes, it is convenient to use it in practice.  
Introducing self-normalization in the context of our algorithm, we switch from equation \ref{E:svrpg.estimate.batch} to:
\begin{align*}
\blacktriangledown J(\vtheta_{t}) := v_t= \wh{\nabla}_N J(\wt{\vtheta})
 + \frac{1}{B} \sum_{i=0}^{B-1} \left[
g(\tau_i|\vtheta_t)\right]\\ 
- \frac{1}{ \sum_{i=0}^{B-1}\omega(\tau_i|\vtheta_t, \wt{\vtheta})} \sum_{i=0}^{B-1} \left[ \omega(\tau_i|\vtheta_t, \wt{\vtheta}) g(\tau_i|\wt{\vtheta})
\right].
\end{align*}
We experienced some improvements using it (see section \ref{sec:exp} for the experimental point of view).

\subsection{Baseline}
As reported in Sec. \ref{subsec:PolicyGradient} a well known variance reduction tool in Reinforcement Learning is the baseline.
This tool does not depend on SVRPG. More precicely we decided to use an Actor Critic baseline, which is a state dependent linear function with a time-varying feature vector \cite{duan2016benchmarking}. Furthermore, the baseline is unique and computed every snapshot using the N trajectories at hand.
